---
title: "Characteristic of Aristotle and Plato School"
subtitle: "Stat 5243 Project 1"
author: "Junhan Huang"
date: "02/06/2023"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---


# Introduction
\ The idea of philosophy first appeared in 800 BC and can be divided geographically into Western philosophy, Eastern philosophy (Indian philosophy) and East Asian philosophy (Chinese philosophy). "THE PHILOSOPHY DATA PROJECT" mainly focuses on the history of Western philosophy and divides it into 13 different schools,  ten of which are core schools called Plato, Aristotle, Rationalism, Empiricism, German Idealism, Communism, Capitalism, Phenomenology, Continental Philosophy, Analytic Philosophy. It is interesting to note that of these ten schools and even of all the major schools of philosophy in the world only two schools are named by philosophers' name, which are Plato and Aristotle. This project will focuses on the characteristic of two schools and conduct sentiment analysis to the two schools.



\newpage


# Table of Content

1. Basic Information 
* Length Analysis
* Frequency Analysis

2. Sentiment Analysis

3. Emotional Analysis

4. Topic Modeling

\newpage



# Basic Information 

## Length Analysis

```{r,  results='hide',  message=FALSE}
library(dplyr)
library(ggplot2)
library(beeswarm)
library(RColorBrewer)
library(data.table)
library(RColorBrewer)
library(patchwork)
library(tm)
library(tidytext)
library(wordcloud)
library(forcats)
library("topicmodels")
```


```{r}
df<-read.csv("~/philosophy_data.csv")
Aristotle<-df%>%filter(df$school=="aristotle")
Plato<-df%>%filter(df$school=="plato")
```

*Because word can represent actual meaning and is not affected by the length of word itself, this project will count the number of word in each sentence and create a new variable named "word_count", without using the sentence length which is the amount of letter and provided by the original dataset. This project presents a comparison not only between the two schools but also with the remaining eight major schools.*

```{r}
df$word_count=lengths(gregexpr("\\W+", df$sentence_str))
df$school_category=ifelse(df$school=="aristotle"|df$school=="plato", df$school, 'other')
```



```{r}
df%>%
  group_by(school_category)%>%
  summarize_at(c('word_count'), c('min', 'mean', 'max', 'sd'))


ggplot(df%>%filter(df$school=="aristotle"|df$school=="plato"), aes(x =word_count, fill=school_category)) + 
  geom_bar( position = position_dodge())+
  labs(x="Word Count", y="Amount of Word Count")+
  theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 1), plot.margin=unit(rep(1,10),'cm'))+
  guides(fill=guide_legend(title="School"))
```

*The dataframe and plot revel that Plato school has shortest mean length of sentence,shortest minimum length of sentence and the lowest standard deviation in the three kinds of school, which might be able to indicate that the Platonist tend to be concise. Moreover, Aristotle school has higher longer mean length and longer max sentence length than Plato school but has shorter max sentence length than the category other.*

## Frequency Analysis

*To analyze the frequency of term in the sentence of the two school, Blank-word removing, Decapitalization, Stop-word removing , Word stemming, Punctuation removing are conducted sequentially as text processing. *

### Aristotle
```{r, warning=FALSE}
Aristotle_corpus = Corpus(VectorSource(Aristotle$sentence_str))
Aristotle_corpus<-tm_map(Aristotle_corpus, stripWhitespace)
Aristotle_corpus<-tm_map(Aristotle_corpus, content_transformer(tolower))
Aristotle_corpus<-tm_map(Aristotle_corpus, removeWords, stopwords("english"))
Aristotle_corpus<-tm_map(Aristotle_corpus, stemDocument, language = "english") 
Aristotle_corpus<-tm_map(Aristotle_corpus, removeWords, character(0))
Aristotle_corpus<-tm_map(Aristotle_corpus, removePunctuation)

Aristotle_tdm_all<-TermDocumentMatrix(Aristotle_corpus)

Aristotle_tdm_tidy=tidy(Aristotle_tdm_all)

Aristotle_tdm_overall=summarise(group_by(Aristotle_tdm_tidy, term), sum(count))

Aristotle_tdm_overall<-rename(Aristotle_tdm_overall, 'count'=`sum(count)`)

Aristotle_tdm_overall<-Aristotle_tdm_overall%>%arrange(desc(count))

Aristotle_tdm_overall$percentage<-Aristotle_tdm_overall$count/sum(Aristotle_tdm_overall$count)

wordcloud(Aristotle_tdm_overall$term, Aristotle_tdm_overall$count,
          scale=c(5,0.5),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(9,"Blues"))
```

```{r, warning=FALSE}
Aristotle_tdm_overall[1:50,] %>%
  mutate(name = fct_reorder(term, percentage)) %>%
  ggplot(aes(x=name, y=percentage)) +
    geom_bar(stat="identity", fill="steelblue2", alpha=.8, width=.4) +
    coord_flip() +
  geom_text(aes(label=paste(round(percentage*100, 3), '%')), vjust=0.5, color="black", size=2.0)+
  theme(axis.text.x = element_text(, hjust = 1, vjust = .5))
```


*From the raw frequency data, the top ten most frequent words in Aristotelian sentence are "one","thing","will","must","also","belong","man","part","good","case", which in real life would have no obvious meaning if they were used alone except the word "good".*


```{r, warning=FALSE}
Aristotle_dtm_tfidf <- DocumentTermMatrix(Aristotle_corpus, control = list(weighting = weightTfIdf))
Aristotle_dtm_tfidf = removeSparseTerms(Aristotle_dtm_tfidf, 0.99)
Aristotle_dtm_tfidf
```


```{r, warning=FALSE}

Aristotle_freq = data.frame(sort(colSums(as.matrix(Aristotle_dtm_tfidf)), decreasing=TRUE))
wordcloud(rownames(Aristotle_freq), Aristotle_freq[,1], 
          scale=c(3,0.5),
          max.words=100, 
          random.order=FALSE,
          random.color=FALSE,
          colors=brewer.pal(1, "Dark2"))
Aristotle_freq
```


* *Instead of th raw frequency data, tf-idf algorithm can measure the relative importance of a word to a corpus. However, the list of ten most important word has no change comparing with the original list.*


### Plato

```{r warning=FALSE}
Plato_corpus = Corpus(VectorSource(Plato$sentence_str))
Plato_corpus<-tm_map(Plato_corpus, stripWhitespace)
Plato_corpus<-tm_map(Plato_corpus, content_transformer(tolower))
Plato_corpus<-tm_map(Plato_corpus, removeWords, stopwords("english"))
Plato_corpus<-tm_map(Plato_corpus, stemDocument, language = "english") 
Plato_corpus<-tm_map(Plato_corpus, removeWords, character(0))
Plato_corpus<-tm_map(Plato_corpus, removePunctuation)

Plato_tdm_all<-TermDocumentMatrix(Plato_corpus)

Plato_tdm_tidy=tidy(Plato_tdm_all)

Plato_tdm_overall=summarise(group_by(Plato_tdm_tidy, term), sum(count))
Plato_tdm_overall<-rename(Plato_tdm_overall, 'count'=`sum(count)`)
Plato_tdm_overall<-Plato_tdm_overall%>%arrange(desc(count))
Plato_tdm_overall$percentage<-Plato_tdm_overall$count/sum(Plato_tdm_overall$count)

wordcloud(Plato_tdm_overall$term, Plato_tdm_overall$count,
          scale=c(5,0.5),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(9,"Blues"))
```

```{r, warning=FALSE}
Plato_tdm_overall[1:50,] %>%
  mutate(name = fct_reorder(term, percentage)) %>%
  ggplot(aes(x=name, y=percentage)) +
    geom_bar(stat="identity", fill="steelblue2", alpha=.8, width=.4) +
    coord_flip() +
  geom_text(aes(label=paste(round(percentage*100, 3), '%')), vjust=0.5, color="black", size=2.0)+
  theme(axis.text.x = element_text(, hjust = 1, vjust = .5))
```




*From the raw frequency data, the top ten most frequent words in Plato school sentence are "one","thing","say","will","now","think","good","must", "man", "make", which in real life would have no obvious meaning if they were used alone except the word "good". There is no doubt that the Platonic list of the top ten most frequent words is not very different from the Aristotelian list, but the different word "say" might introduce some information.*

```{r, warning=FALSE}
Plato_dtm_tfidf <- DocumentTermMatrix(Plato_corpus, control = list(weighting = weightTfIdf))
Plato_dtm_tfidf = removeSparseTerms(Plato_dtm_tfidf, 0.99)
Plato_dtm_tfidf
```
```{r, warning=FALSE}
Plato_freq = data.frame(sort(colSums(as.matrix(Plato_dtm_tfidf)), decreasing=TRUE))
wordcloud(rownames(Plato_freq), Plato_freq[,1], 
          scale=c(3,0.5),
          max.words=100, 
          random.order=FALSE,
          random.color=FALSE,
          colors=brewer.pal(1, "Dark2"))

Plato_freq
```


* *Unlike the minor difference after conducting tf-idf algorithm in the Aristote part, the list gained from tf-idf algorithm has one informative word "socrates", which is a famous ancient Greek philosopher. The word "socrates" introduce taht there might be a possible relationship between Aristotle's school and the socrates school*


# Sentiment Analysis

*Sentiment has three category which are negative, neutral and positive. By conducting the sentiment analysis, each sentence will be labeled the sentiment and the proportion of each category of sentiment can overall revel the main sentiment of each school. *
```{r, warning=FALSE}
library(sentimentr)

Aristotle_sentiment<-sentiment(Aristotle$sentence_str)
Plato_sentiment<-sentiment(Plato$sentence_str)
```
```{r}
Aristotle_sentiment_df <- setDF(Aristotle_sentiment)
Plato_sentiment_df <- setDF(Plato_sentiment)
#Function that generates a sentiment class based on sentiment score
get_sentiment_class <- function(sentiment_score) {
  
  sentiment_class = "Positive"
  
  if ( sentiment_score < -0.3) {
    sentiment_class = "Negative"
  } 
  
  else if (sentiment_score < 0.3) {
    sentiment_class = "Neutral"
  }
  
  sentiment_class
}
#add a sentiment_class attribute
Aristotle_sentiment_df$sentiment_class <- 
        sapply(Aristotle_sentiment_df$sentiment,get_sentiment_class)
Plato_sentiment_df$sentiment_class <- 
        sapply(Plato_sentiment_df$sentiment,get_sentiment_class)
```

```{r}
Aristotle_sentiment_summary <- count(Aristotle_sentiment_df, sentiment_class)
Aristotle_sentiment_summary$freq<-Aristotle_sentiment_summary$n/sum(Aristotle_sentiment_summary$n)
Plato_sentiment_summary <- count(Plato_sentiment_df, sentiment_class)
Plato_sentiment_summary$freq<-Plato_sentiment_summary$n/sum(Plato_sentiment_summary$n)


par(mfcol=c(1,2), pin = c(3.5,3))
pie(Aristotle_sentiment_summary$freq, 
    labels=paste(Aristotle_sentiment_summary$sentiment_class, '\n',100*round(Aristotle_sentiment_summary$freq, 3), "%"),
    col=brewer.pal(nrow(Aristotle_sentiment_summary), "Blues"), 
    main='Aristotle Sentiment')
pie(Plato_sentiment_summary$freq, 
    labels=paste(Plato_sentiment_summary$sentiment_class, '\n', 100*round(Plato_sentiment_summary$freq, 3), "%"),
    col=brewer.pal(nrow(Plato_sentiment_summary), "Blues"), 
    main='Plato Sentiment')
```

* *It is easy to find that the majority sentiment of Aristotle and Plato is Neutral which are 81.7% in Aristotle's and 74.8% in Plato's, and the positive statements in the explicitly biased statements always outnumber the negative statements in both schools. Consequently, the sentiment analysis can draw a conclusion that the sentiment characteristic of each school is mostly unbiased and is positive in the biased section.*

# Emotional Analysis

*Because of the majority sentiment of both schools is neutral, it is obvious that sentiment analysis alone is not enough to tell people about the characteristics of the two schools. Consequently, emotional analysis is conducted which detect the emotional rate of each word in sentences and label words with the sixteen category: anger, anticipation, disgust, fear, joy, sadness, surprise, trust and their negated part.*
```{r, warning=FALSE}
Aristotle_emotion<-emotion_by(Aristotle$sentence_str)
Plato_emotion<-emotion_by(Plato$sentence_str)
```

```{r}
Aristotle_emotion_summary=subset(
                  aggregate(emotion_count  ~ emotion_type , 
                                 Aristotle_emotion, sum),
                   emotion_count > 0 )
Aristotle_emotion_summary$freq<-Aristotle_emotion_summary$emotion_count/sum(Aristotle_emotion_summary$emotion_count)

Plato_emotion_summary=subset(
                  aggregate(emotion_count  ~ emotion_type , 
                                 Plato_emotion, sum),
                   emotion_count > 0 )
Plato_emotion_summary$freq<-Plato_emotion_summary$emotion_count/sum(Plato_emotion_summary$emotion_count)
```

```{r, warning=FALSE}

p1<-ggplot(Aristotle_emotion_summary, aes(x=Aristotle_emotion_summary$emotion_type, y=Aristotle_emotion_summary$freq))+
  geom_bar(stat = "identity", fill="steelblue")+
  labs(x='Emotion Type', y='Percentage', title = "Aristotle Emotion Summary")+
  geom_text(aes(label=paste(round(freq*100, 3), '%')), vjust=1.6, color="white", size=2.0)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))

p2<-ggplot(Plato_emotion_summary, aes(x=Plato_emotion_summary$emotion_type, y=Plato_emotion_summary$freq))+
  geom_bar(stat = "identity", fill="steelblue")+
  labs(x='Emotion Type', y='Percentage', title = "Plato Emotion Summary")+
  geom_text(aes(label=paste(round(freq*100, 3), '%')), vjust=1.6, color="white", size=2.0)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))

p1+p2
```

*From the summary of two schools, trust is major emotion of words in both schools which might be able to indicate both of two schools are making statement about what they believe. There is one difference that Aristotle's sentences contain more aniticipation words than joy words but Plato's sentences contain more joy words than aniticipation words. The major identical emotional aniticipation and minor emotion difference might be able to explain why Plato School initially originate from Aristotle school but finally evolve as a different brunch of philosophy. *

# Conclusion 

*As the oldest school and the only two philosophical schools named after people, Aristotle's School and Plato's School have very different characteristics in length but similar characteristics of word frequency. On the other hand, the two colleges share similar sentiment and emotional characteristics, neutral and trust, but also have slightly different emotional characteristics which is the rank of anticipation and joy. The difference might explains the difference of  their viewpoint. To understanding the detail of difference between their viewpoint, topic modeling might be needed in future project.* 

